---
title: "Assignment 1"
author: "Emily Aaron"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I have completed 11/15 questions for assignment 1.


# Question 1

Assignments-15%
Labs-10%
Projects-10%
In Class Quiz-10%
Chapter Quizzes-5%
Mid-Term Exam-20%
Final-30%
A-90s
B-80s
C-60s & 70s
D-50s
F->50

# Question 2
```{r}
getwd()
ddt<-read.csv("DDT.csv")
head(ddt)
```

(a)
```{r}
rivcol=with(ddt, ifelse(RIVER=="FCM","Green",
                        ifelse(RIVER=="LCM","red",
                               ifelse(RIVER=="SCM","Black", rainbow(4)))))
coplot(LENGTH~WEIGHT|RIVER*SPECIES, data=ddt, col=rivcol)
```


(b) 
(c) Line A changes the factor Mile into a numeric vector.
(d)Line B gives the unique values of the vector.
(e) The rivers FCM, LCM, and SCM only contain one species of fish which is CCATFISH.
(f) The mean is 45
```{r}
ddt[ddt$RIVER=="FCM"& ddt$SPECIES=="CCATFISH"]
```



# Question 3

(a) qualitative
(b) qualitative
(c) quantitative
(d) qualitative
(e) quantitative
(f) qualitative
(g) quantitative

# Question 4

(a) Simple random sample, stratified random sampling, cluster sampling, systematic sampling

(b) Simple random sample is when each variable used as an equal chance of being selected for the experiment.
Stratified random sampling is the units that can be separated into two groups where they units are similar within the groups rather than across. 
Cluster sampling is natural groupings that data is collected from.
Systemic sampling is choosing every specific kth unit from the list given.

# Question 5

```{r}
mtbe = read.csv("C:/users/eaaro/Documents/Stats/Labs/MTBE.csv", header=TRUE)
head(mtbe)
dim(mtbe)
ind=sample(1:223, 5, replace=FALSE)
mtbe[ind,]
```

(a)
```{r}
mtbeo=na.omit(mtbe)
depth=mtbeo[mtbeo$Aquifier=="Unconsoli",]$Depth
sd(depth)
```

#Question 6

```{r}
ethqke= read.csv("C:/users/eaaro/Documents/Stats/Labs/EARTHQUAKE.csv", header = TRUE)
dim(ethqke)
eq= sample(1:2929, 30, replace = FALSE)
ethqke[eq,]
```

(a)
  (i)
```{r}
plot(ts(ethqke$MAG))
```

  (ii)
```{r}
median(ethqke$MAGNITUDE)
```

# Question 7

(a) Designed experiment
(b) All fish in Tennessee Rivers and its tributaries.
(c) Location and species

# Question 8

(a) Bar plot
(b) Robotic limbs 
(c) Legs only robot design
(d) None; 0.1415
  Both:0.0755
  Legs Only:0.5943
  Wheels only: 0.1887
(e)
```{r}
freq=c(15,8,63,20)
RL=c("None","Both","LegsO", "WheelsO")
l=rep(RL,freq)
pareto<-function(x,mn="Pareto barplot",...){  # x is a vector
x.tab=table(x)
xx.tab=sort(x.tab, decreasing=TRUE,index.return=FALSE)
cumsum(as.vector(xx.tab))->cs
length(x.tab)->lenx
bp<-barplot(xx.tab,ylim=c(0,max(cs)),las=2)
lb<-seq(0,cs[lenx],l=11)
axis(side=4,at=lb,labels=paste(seq(0,100,length=11),"%",sep=""),las=1,line=-1,col="Blue",col.axis="Red")
for(i in 1:(lenx-1)){
segments(bp[i],cs[i],bp[i+1],cs[i+1],col=i,lwd=2)
}
title(main=mn,...)
}
pareto(l)
```

# Question 12

```{r}
pip= c(1.72,2.50,2.16,2.13,1.06,2.24,2.31,2.03,1.09,1.40,2.57,2.64,1.26,2.05,1.19,2.13,1.27,1.51,2.41,1.95)
mean(pip)
sd(pip)
```
The interval for pipe roughness will be 1.881 +/- 2(0.5239).

# Question 13

(a)
```{r}
gob=read.csv("C:/users/eaaro/Documents/Stats/Data/GOBIANTS.csv")
mean(gob$AntSpecies)
median(gob$AntSpecies)
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
v<-c(gob$AntSpecies)
getmode(v)
```

The mean number of ant species in Mongolia is 12.82 meaning that this is the average of the data set.
The median of the set is 5, where this is the middle of the data set.
The mode is 5 which is the most common number in the data set.

(b) The median would be a preferred measure of central tendency since there is a skewness taking place due to two larger variables in the set.

(c) 
```{r}
ds= c(40,52,40,43,27)
mean(ds)
getmode(ds)
median(ds)
```

(d)
```{r}
gd=c(30,16,30,56,22,14)
mean(gd)
median(gd)
getmode(gd)
```

(e) Yes, because the Dry Steppe has total plant cover that is more similar to each other and the Gobi Desert has one outlier that affects the data set.

# Question 14

(a)
```{r}
gal=read.csv("C:/users/eaaro/documents/Stats/Data/GALAXY2.csv")
v<- gal$VELOCITY
h<-hist(v,xlab="Velocity km/s", main="Histogram of Velocity")
xfit<-seq(min(v),max(v),length=25000)
yfit<-dnorm(xfit,mean=mean(v), sd=sd(v))
yfit<- yfit*diff(h$mids[1:2])*length(v)
lines(xfit, yfit, col="red")
```

(b) Yes it supports the double cluster theory because there are two peaks 

(c) First cluster
```{r}
gv<-sort(v)
a1<-c(gv[1:21])
mean(a1)
sd(a1)
```
Second Cluster
```{r}
gv<-sort(v)
a2<-c(gv[22:51])
mean(a2)
sd(a2)
```

(d) A galaxy velocity of 20,000 km/s will belong to A1775A since it is between 18,000 and 21,000 km/s.
