---
title: 'Assignment 2'
author: "Emily Aaron"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

I have completed 12/17

# Questions{}

## Q1 (3.36)

### a.) Expert fails matched prints
P(Expert Fails)=1-P(Expert Matches)
1-0.9212=0.0788

### b.) Novice fails matched prints
P(Novice Fails)=1-P(novice matches)
1-0.7455=0.2545

### c.) Random Select
Based on the above probabilities, the novice is more likely to be picked since they have a higher chance of failing when the prints are matched.

## Q2 (3.52)

### a.) Probability of a Positive Test
A- athletes that test positive
B- user athletes that test positive
$$
\begin{equation}
P(A\mid B)= \frac{P(A)P(A\mid B)}{P(B)}
\end{equation}
$$
$$
\begin{equation}
P(A\mid B) = \frac{50}{100}
\end{equation}
$$
$$
\begin{equation}
P(B)= \frac{100}{1000}
\end{equation}
$$
$$
\begin{equation}
P(A)=\frac{59}{1000}
\end{equation}
$$
$$
\begin{equation}
P(A\mid B)=\frac{\frac{59}{1000}\frac{50}{100}}{\frac{100}{1000}}
\end{equation}
$$
$$
\begin{equation}
P(A\mid B)=\frac{59}{200}=0.295
\end{equation}
$$

### b.) Probability of a Negative Test
A-Negative Test
B-Athlete is nonuser
$$
\begin{equation}
P(A\mid B)= \frac{P(A\cap B)}{P(B)}
\end{equation}
$$
$$
\begin{equation}
P(A\cap B)= \frac{1000-100-9}{1000}
=\frac{891}{1000}
\end{equation}
$$
$$
\begin{equation}
P(E)=\frac{1000-100}{1000}
=\frac{900}{1000}
\end{equation}
$$
$$
\begin{equation}
P(A\mid B)= \frac{P(A\cap B)}{P(E)}
=\frac{\frac{891}{1000}}{\frac{900}{1000}}
=0.99
\end{equation}
$$

### c.) Bayes' Rule for actual doping
A1-Drug User
A2-Non user
B-Positive Test
$$
\begin{equation}
P(A_1\mid B)=\frac{P(A_1)P(B\mid A_1)}{P(A_1)(B\mid A_1)+P(A_2)P(B\mid A_2)}
\end{equation}
$$
$$
P(A_1)P(B\mid A_1)=\frac{100}{1000}\frac{50}{100}=\frac{1}{20}
$$
$$
\begin{equation}
P(A_2)P(B\mid A_2)=\frac{900}{1000}\frac{9}{900}=\frac{9}{1000}
\end{equation}
$$
$$
\begin{equation}
P(A_1\mid B ) = \frac{\frac{1}{20}}{\frac{1}{20}+\frac{9}{1000}}=\frac{50}{59}=0.8475
\end{equation}
$$

## Q3

## Q4 (Theorem 3.2 Proof)
Assume there are n elements to choose from N

N is the number of ways they can be arranged to the nth
$$
\begin{equation}
N(N-1)(N-2)(N-3)....(N-n+1)
\end{equation}
$$
Then N! is defined as N(N-1)(N-2)...(3)(2)(1) we'll use the multiplicative rule for (N-n)(N-n-1)...(3)(2)(1)
$$
\begin{equation}
\frac{N(N-1)(n-2)...(N-n+1)(N-n)(N-n-1)...(3)(2)(1)}{(N-n)(N-n-1)...(3)(2)(1)}
\end{equation}
$$
$$
\begin{equation}
P^N_n= \frac{N!}{(N-n)!}
\end{equation}
$$
## Q5

## Q6

## Q7 (4.2)

### a.) All Probabilities of Y =1
$$
\begin{equation}
\sum P(y)=0.09+0.3+0.37+0.2+0.04=1
\end{equation}
$$

### b.) 3/4 of Homes exceeds dust mite level
$$
\begin{equation}
P(3)+P(4)=0.2+0.04=0.24
\end{equation}
$$

### c.)P(<2) of homes exceeds dust mite level
$$
\begin{equation}
P(y<2)=0.09+0.3=0.39
\end{equation}
$$

## Q8 (4.12)

### a.)Sum of Probabilites =1
```{r}
sum(0.17,0.1,0.11,0.11,0.1,0.1,0.07,0.05,0.03,0.02,0.02,0.02,0.02,0.02,0.01,0.01,0.01,0.01,0.01,0.005,0.005)
```

### b.) P(Y>=10)
```{r}
sum(0.02,0.02,0.02,0.02,0.01,0.01,0.01,0.01,0.01,0.005,0.005)
```

### c.) Mean and Variance
$$
\begin{equation}
E(Y)=\sum Y\times P(Y)
=0(.17)+1(.1)....+20(.0005)=4.655
\end{equation}
$$
$$
\begin{equation}
V(Y)=\sum Y^2P(Y)-mean^2=19.856
\end{equation}
$$

## Q9 (4.34)

### a.) P(Y=10)
```{r}
dbinom(10,25,0.7)
```

### b.) P(Y=<5)
```{r}
sum(dbinom(0,25,0.7),dbinom(1,25,0.7),dbinom(2,25,0.7),dbinom(3,25,0.7),dbinom(4,25,0.7),dbinom(5,25,0.7))
```

### c.) Mean and Standard deviation
```{r}
25*0.7
```
```{r}
sqrt(25*.7*.3)
```

### d.) Interpretation
Based on part c, about 18 students will finish their degree out of the 25 with a deviation of 2.29.

## Q10 (4.46)

### a.) 5 trials are assigned to 10 tracks
```{r}
N<-factorial(50)/(factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5)*factorial(5))
N/(10^50)
```

### b.) P(x<2)
```{r}
dbinom(0,50,0.1)+dbinom(1,50,0.1)
```

## Q11 (4.54)

### a.) Probability distribution of Y
$$
\begin{equation}
P(Y=k)=p(1-p)^{k-1}
\end{equation}
$$

### b.) E(Y)
```{r}
1/0.4
```
It would take about 3 people to say something on than the information given.

### c.) P(Y=1)
```{r}
0.4*(1-0.4)^0
```

### d.) P(Y>2)
```{r}
1-((.4*.6^0)+.4*.6^1)
```


## Q12 (4.66)

### a.) Expected Number
$$
\begin{equation}
\mu = \frac{n\times r}{N}=\frac{10\times 8}{209}=0.38
\end{equation}
$$

### b.) P(4) treat hazardous materials
$$
\begin{equation}
P(4)= \frac{\binom 84 \binom {201}{6}}{\binom {209}{10}}=0.00017
\end{equation}
$$

## Q13 (4.78)

### a.) V(Y)
V(Y)=0.3

### b.)Poisson Assumption
The probability that an event happens is the same for all them. The area or time is independent of other units. The experiment counts Y of an event occuring.

### c.) No casualities in 3 years
```{r}
(.03^0*exp(-.03))/factorial(0)
```


## Q14 (5.2)

### a.) Value of C
$$
\begin{equation}
\int^1_0 c(2-y)dy=1
\end{equation}
$$
$$
\begin{equation}
c[2y-\frac {y^2}{2}]^1_0=1
\end{equation}
$$
$$
\begin{equation}
c=\frac23
\end{equation}
$$

### b.) Cumulative distribution
$$
\begin{equation}
F(y)= \int^y_{-\infty} \frac23 (2-t)dt
\end{equation}
$$
$$
\begin{equation}
\frac23 [2t-\frac {t^2}{2}]^y_0
\end{equation}
$$

### c.) F(0.4)
```{r}
0.4^2/2
2*.4-.08
0.72*(2/3)
```

### d.) P(0.1=<Y=<0.6)
```{r}
(2/3)*(2*.6-(.6^2/2))-(2/3)*(2*.1-(.1^2/2))
```


## Q15 (5.10)

## Q16 (5.36)

### a.) Alkalinity level over 45 mg/L
P(x<55)
```{r}
1-pnorm(-1.5625)
```

### b.) Below 55 mg/L
P(x<55)
```{r}
pnorm(1.5625)
```

### c.) Between 51 and 52 mg/L
P(51<x<52)
```{r}
pnorm(0.625)-pnorm(0.3125)
```

## Q17 (5.38)